Halo alignments with large scale tidal and velocity fields

### 2013-05-01 paper/main.tex
adding text to the tables

... Table 1 summarizes recent results found in the literature for
shape and angular momentum alignment.

@@

\begin{table}
\begin{tabular}{llll}
Author & Web Method & Halo Finder & SPIN \\
\end{tabular}
SPIN
\end{table}

@@

\item
\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for mutual alignment of angular momentum vectors, and
alignment with structure. halos on any escale by close pair
statistics. They don't find any evidence for a statistically significant mutual
alignment of haloes on any scale,
\end{itemize}
\section{N-body simulation and halo finding}

>>>>

... Table 1 and Table 2 summariz recent results found in the literature for
shape and angular momentum alignment, respectively.

@@

\begin{table}
\begin{tabular}{lllll}
Author & Web Method & Halo Finder & Major Axis & Correlation\\
\end{tabular}
SHAPE
\end{table}

TABLA
\begin{table*}
\begin{tabular}{ccccccc}\hline\hline
Author & Web Method & Halo Finder & Spatial Scale & Test Direction &
Alignment & Mass dependence\\\hline
\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc & along
the filament & $-$& none\\
\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc &
perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\
\cite{Hatton2001} & Neighbors$^1$ & FOF & & & 0\\\hline\hline
\end{tabular}\\
\caption{Summary of previous theoretical results.
NOTES:
$^1$ They do not use a web finder method. They look for correlations
with neightborig structures on any escale.
Angular Momentum}
\end{table*}

@@

\item
\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for alignment of angular momentum vectors with neighbohring structures or other massive structures. They match halos using close pair statistics. They do not find any evidence for a statistically significant mutual alignment of halos on any escale.
\end{itemize}
\section{N-body simulation and halo finding}
